





*************


Complex arithmetic operations are referred to simply as genetic engineering
**********
Time delay neural network (TDNN) is a multilayer artificial neural network architecture whose purpose is to 1) classify patterns with shift-invariance, and 2) model context at each layer of the network.
***************
LibROSA is a python package for music and audio analysis. It provides the building blocks necessary to create music information retrieval systems.

For a quick introduction to using librosa, please refer to the Tutorial. For a more advanced introduction which describes the package design principles, please refer to the librosa paper at SciPy 2015.
********************


***************
What is Kaldi? Kaldi is a state-of-the-art automatic speech recognition (ASR) toolkit, containing almost any algorithm currently used in ASR systems. It also contains recipes for training your own acoustic models on commonly used speech corpora such as the Wall Street Journal Corpus, TIMIT, and more.
https://kaldi-asr.org/doc/versions.html

 
***************
What is HMM model in speech recognition?
Hidden Markov model (HMM) is the base of a set of successful techniques for acoustic modeling in speech recognition systems. The main reasons for this success are due to this model's analytic ability in the speech phenomenon and its accuracy in practical speech recognition systems.

******
What is a Gaussian HMM?
The Gaussian hidden Markov model (Gaussian HMM) is a type of finite-state-space and homogeneous HMM where the observation probability distribution is the normal distribution, where and are mean and covariance parameters at state .7 Aug 2020
**************
What is LSTM and why is used?
Long Short-Term Memory (LSTM) networks are a type of recurrent neural network capable of learning order dependence in sequence prediction problems. This is a behavior required in complex problem domains like machine translation, speech recognition, and more. LSTMs are a complex area of deep learning.
*******************************

\[ \prod_{i=a}^{b} f(i) \]