\section{Problem definition} \label{problem}

In this chapter, we introduce the problem this thesis addresses and define the scope of our work. We also formalize the problem by formulating a research question, and present the approaches we will implement.

The problem, presented in section \ref{problem_intro}, arises from the poor quality of the subjects that are currently present in the repositories. 81 \% of all subjects are only assigned to one document, and only 5 \% of the subjects are assigned to more than three documents. This makes it hard to navigate the repositories by filtering the documents by subject, which is the purpose of having subjects. The sets of subjects are also different for each repository, which hinders the interoperability.

In section \ref{problem_scope} we define the scope of this thesis. We only consider the titles and abstracts of theses and publications written in English, which reduces the complexity of the task without hindering its research interest. We also restrict ourselves to evaluating methods that use an existing set of subjects. We use the subjects extracted from  the \acrfull{mag}, which is able to identify the relevant concepts in science because of its size. These subjects can then be used for any multidisciplinary repository, other than those included in our experiments.

Once the problem and scope have been introduced, we formalize the problem by formulating the research question this thesis attempts to answer, in section \ref{problem_rq}. This thesis focuses on the evaluation of supervised and unsupervised algorithms for performing \acrlong{si} in small and multidisciplinary repositories. 

\input{problem/intro}
\input{problem/scope}
\input{problem/rq}
