\section{Repository analysis} \label{repo_analysis}

This thesis comprises the documents on the repositories of the \acrshort{tu}, \acrshort{hu} and \acrshort{fu}. The repositories are called depositonce, edoc and refubium, respectively. There are 62,507 documents\footnote{As of 26/05/2021.} among the three repositories. As mentioned in section \ref{problem_scope_docs}, we are only interested in theses and publications written in English. We thus discard documents referring to research data, university related documents and others, leaving us with 29,399 documents, with 47 \% of them belonging to refubium and 63 \% being publications. The analysis presented in this chapter only considers these relevant documents.

We start by exploring the existing subjects in section \ref{repo_analysis_subjects}, which are at the core of this thesis. 81 \% of them appear in only one document, and only 5 \% in more than three, which renders them useless for navigating the repositories. We also present the distribution of the \acrfull{ddc} subjects. \textit{Science}, \textit{Social Sciences} and \textit{Technology} cover 83 \% of all the relevant documents.

We then look at venues (section \ref{repo_analysis_venues}) and contributors (section \ref{repo_analysis_contributors}), which are also useful to relate documents to one another. Venues are assigned to four documents on average, and only 2 \% of the publications don't have one. Referees and advisors, which we will use as a replacement for venues when considering theses, also offer a good coverage of the theses, with all but 4 \% of the theses having an advisor or a referee.

Finally, in section \ref{repo_analysis_data}, we analyze the actual data that will be used to perform \acrshort{si}: the titles and abstracts of the documents. All documents in the repositories are required to have a title, so all the documents have one. Abstracts, on the other hand, are optional. 6 \% of the relevant documents don't have one. In this final section, we also discuss how certain titles and abstracts are tagged as being written in English when they are not. When running a language detection algorithm, we find out that 320 abstracts are not actually written in English. We try to solve this issue for detecting the language of the other abstracts of the documents, which are tagged as being written in other languages.

\input{repo_analysis/subjects}
\input{repo_analysis/venues}
\input{repo_analysis/contributors}
\input{repo_analysis/titles_and_abstracts}
