\section{Related work on unsupervised approaches} \label{subject_indexing}

\acrfull{si} has been a topic in academia well before it became important in the digital realm, as it was relevant for the organization of conventional libraries. The current ISO standard (ISO 5963:1985) defines \acrshort{si} as a three-step process:

\begin{enumerate}
    \item Determine the content of a document.
    \item Perform conceptual analysis to extract concepts from the content.
    \item Translate the concepts into a controlled vocabulary.
\end{enumerate}

Automatic Subject Indexing (ASI) occurs when machines perform this \acrshort{si} procedure instead of humans. There are also approaches in which machines aid humans in the process of indexing, called Machine-Aided Indexing (MAI) or Computer-Aided Indexing (CAI). We will however refer to the automatic task as \acrshort{si}, which is how it is usually referred to in the literature. Indexing can be differentiated from classification in its purpose \cite{golub2019automatic}. It focuses on facilitating the retrieval of a document, assuming that users will look for it from different perspectives. Classification, on the other hand, tries to clearly categorize the documents, using fewer subjects per document and aiming for the highest precision instead of covering a broader spectrum of possible queries.

In this chapter, we review the literature on this topic. We first summarize the different ways in which \acrshort{si} methods can be classified, which revolve around two conditions: the existence of training data, which enables the implementation of supervised \acrlong{ml} algorithms, and the availability of a set of subjects. If such a set does not exist, the subjects must be extracted from the texts.

Afterwards, we present the common challenges that \acrshort{si} methods face. Heterogeneous documents increase the complexity of performing \acrshort{si}, whereas the number of documents hinders the performance of many methods. Also, texts written in different styles pose different problems. Subjects can also pose challenges, such as their uneven assignment distribution and how their distribution changes over time. Training data may also suffer from this distribution drift over time, as well as label noise due to inconsistencies between different human indexers.

In the next section, we present several unsupervised approaches to \acrshort{si} that use an existing set of subjects. We first present two approaches that are popular in the literature: string matching methods that map subjects to documents, relying on the quality of the set of subjects to achieve a high matching rate, and the application of \acrlong{lda} for subject indexing scenarios where subjects already exist.

We then present the \acrfull{mag} in section \ref{subject_indexing_mag}. The \acrshort{mag} is, to the best of our knowledge, the most successful application of unsupervised subject indexing for scientific texts. Its use case closely resembles ours, as their dataset comprises documents from various scientific fields. They are also the source for our set of subjects. Their indexing procedure consists of vectorizing documents and subjects and computing the cosine distances between them to discover the similarity between each document and each subject. In this thesis, we implement the \acrshort{mag} indexing procedure, as its scenario closely resembles ours, and it is proven to be accurate. The other approaches discussed in this chapter neither as accurate, nor as well tested for scientific texts. The \acrshort{mag} is widely used in academia to this day, so we safely assume its indexing method was successful.

\input{subject_indexing/types}
\input{subject_indexing/challenges}
\input{subject_indexing/examples}
\input{subject_indexing/mag}
